Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-04-18 finalReportPres.tex
Added detailed NN Simulink blocks for steering and accel
Updated Final Presentation

\begin{frame}{Validation and Testing}{Validation Setup}
	\begin{figure}
		\centering \includegraphics[width=.45\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}\quad%
		\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{itemize} \item HIL Bench 						\item Measuring output voltages to confirm results \end{itemize} \end{minipage}\\[1em]
		\centering \includegraphics[angle=270,width=.45\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}\quad%
		\centering \includegraphics[angle=270,width=.45\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
	\end{figure}
\end{frame}

>>>>

\begin{frame}{Validation and Testing}{Validation Setup}
	\begin{figure}
		\centering \includegraphics[width=.35\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}\quad%
		\centering \begin{minipage}[b][0.35\textheight][c]{.35\linewidth} \begin{itemize} \item HIL Bench 						\item Measuring output voltages to confirm results \end{itemize} \end{minipage}\\[1em]
		\centering \includegraphics[angle=270,width=.35\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}\quad%
		\centering \includegraphics[angle=270,width=.35\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
	\end{figure}
\end{frame}
